---
title: "3.1 - Introduction to Differentiation"
output: webexercises::webexercises_default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(webexercises)
```


```{r, echo = FALSE, results='asis'}
# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple")
```

To check your understanding, work through this interactive exercise and ask for help with anything you are stuck on or that you don't understand.

\begin{center}
    \begin{tabular}{cc}
        hey & hi\\
    \end{tabular}
\end{center}

## Tangents to a Curve {-}

$$\dfrac{2}{5}$$

A **tangent** is a straight line which `r mcq(c("crosses","doesn't meet",answer="touches","meets"))` a curve at a point. 

Shown below are a **line** and a **curve**. Use the slider to change the *gradient* of the line until it becomes a **tangent** to the curve at the point $\left(7,3\right)$. 

The gradient of the **tangent** to the curve at the point $\left(7,3\right)$ is: $m=$`r fitb(2)`

The blanks are case-sensitive; if you don't care about case, use the argument `ignore_case = TRUE`.

What is the letter after D? `r fitb("E", ignore_case = TRUE)`

If you want to ignore differences in whitespace use, use the argument `ignore_ws = TRUE` (which is the default) and include spaces in your answer anywhere they could be acceptable.


"Never gonna give you up, never gonna: `r mcq(c("let you go", "turn you down", "run away", answer = "let you down"))`"

"I `r mcq(c(answer = "bless the rains", "guess it rains", "sense the rain"))` down in Africa" -Toto

True or False? You can permute values in a vector using `sample()`. `r torf(TRUE)`


`r opts_p <- c(
   "the probability that the null hypothesis is true",
   answer = "the probability of the observed, or more extreme, data, under the assumption that the null-hypothesis is true",
   "the probability of making an error in your conclusion"
)`

`r longmcq(opts_p)`

**What is true about a 95% confidence interval of the mean?**

`r opts_ci <- sample(c(
  answer = "if you repeated the process many times, 95% of intervals calculated in this way contain the true mean",
  "there is a 95% probability that the true mean lies within this range",
  "95% of the data fall within this range"
))`

`r longmcq(opts_ci)`

## Checked sections

Create sections with the class `webex-check` to add a button that hides feedback until it is pressed. Add the class `webex-box` to draw a box around the section (or use your own styles).

::: {.webex-check .webex-box}

I am going to learn a lot: `r torf(TRUE)`

```{r, results='asis'}
opts <- c(
   "the probability that the null hypothesis is true",
   answer = "the probability of the observed, or more extreme, data, under the assumption that the null-hypothesis is true",
   "the probability of making an error in your conclusion"
)

cat("What is a p-value?", longmcq(opts))
```

:::

## Hidden solutions and hints

You can fence off a solution area that will be hidden behind a button using `hide()` before the solution and `unhide()` after, each as inline R code.  Pass the text you want to appear on the button to the `hide()` function.

If the solution is an RMarkdown code chunk, instead of using `hide()` and `unhide()`, simply set the `webex.hide` chunk option to TRUE, or set it to the string you wish to display on the button.

**Recreate the scatterplot below, using the built-in `cars` dataset.**

```{r}
with(cars, plot(speed, dist))
```


`r hide("I need a hint")`

See the documentation for `plot()` (`?plot`)

`r unhide()`


<!-- note: you could also just set webex.hide to TRUE -->

```{r, echo = TRUE, eval = FALSE, webex.hide="Click here to see the solution"}
plot(cars$speed, cars$dist)
```

