---
title: "Quadratic Inequations"
output: webexercises::webexercises_default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(webexercises)
```


```{r, echo = FALSE, results='asis'}
# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple")
```

Quadratic **equations** in the Higher course will typically be solved by **factorising**; the use of other valid methods such as the *quadratic formula* is permitted but not required.


**quadratic inequations**

<script src="https://www.geogebra.org/apps/deployggb.js"></script>
<div id="around">
<div id="ggb-element"></div></div>
<script>
    var params = {"borderRadius":5,"filename":"HM04.1QuadraticInequations1.ggb", "showResetIcon": true};
    var applet = new GGBApplet(params, true);
    window.addEventListener("load", function() {
        applet.inject('ggb-element');
    });
</script>

## Fill-In-The-Blanks (`fitb()`)

Create fill-in-the-blank questions using `fitb()`, providing the answer as the first argument.

- 2 + 2 is `r fitb(4)`

You can also create these questions dynamically, using variables from your R session.

```{r}
x <- sample(2:8, 1)
```

- The square root of `r x^2` is: `r fitb(x)`


